---
layout: post
title: Read ALL the Papers!
author: "Eric Sodomka"
date: "May 5, 2016"
output: 
  html_document
---

<!---
(NOTE: If you have stumbled upon this post, you're reading a rough draft that I'm playing around with for setting up this blog. Everything here is subject to change. Continue reading at your own peril.)
--->



```{r echo = FALSE}
ec_start_date <- as.Date('2016-07-24')
acceptance_date <- as.Date('2016-05-10')
camera_ready_date <- as.Date('2016-05-30')
start_date <- as.Date('2016-05-30')
# EC2015 acceptances: 72 (http://dl.acm.org/citation.cfm?id=2764468)
num_papers <- 72 

# assuming I start reviewing from acceptance date, and end with some buffer
# before the EC start date.
days_buffer <- 7
days_available <- as.numeric(ec_start_date - start_date) - days_buffer
papers_per_day <- num_papers / days_available
```

Back when I was a snot-nosed intern for [Sébastien Lahaie](http://slahaie.net/), I remember a lunchtime group conversation about somebody that had supposedly *read every paper* prior to attending a particular conference. 

I don't remember the name of this person or the conference---perhaps someone who was there can fill in the details in the comments section---and I also don't know if this diligent reader is actually one of many. 

But the idea has stuck with me, perhaps because it's so different from my own, and I think most others', pre-conference routines. At my best, I'll skim a paper or two the night before the conference (but more likely than not, I'll still be scrambling with slides).

[NOTE: You've stumbled upon a incomplete draft of a blog post. Continue reading at your own peril, or check in later for a properly published version.]

This time around, I'm going to put on my reality distortion glasses and try to avoid past behavior predicting future behavior. **My wacky idea for EC 2016 is to try to "read" and "summarize" every paper by the start of the conference** on `r ec_start_date`. 

I've added quotes to acknowledge that both my readings and summaries may be intolerably shallow on the first pass, given the limited amount of time until the conference and the fact that this is not a substitute for my regular workday. 
I also suspect that, for a researcher wishing to advance the state of the art in a particular area, diving deeply into a handful of relevant papers may be more fruitful than the breadth-first approach I'm exploring here.

Regardless, it sounds like a fun thing to try. My hope is that, by the end, I will have a better sense of the bigger picture than I've had previously, and that reading in advance will allow me to better absorb the material in the talks.

## How to Read a Paper?

[S. Keshav](http://blizzard.cs.uwaterloo.ca/keshav/wiki/index.php/Main_Page)'s article on [How to Read a Paper](http://blizzard.cs.uwaterloo.ca/keshav/home/Papers/data/07/paper-reading.pdf) (pdf). He also has a good collection of other [research advice](http://blizzard.cs.uwaterloo.ca/keshav/wiki/index.php/Advice).

[Michael Littman](http://cs.brown.edu/~mlittman/) says to start with the figures and try drawing your own conclusions before you see what the authors say about their results.




## The Game Plan: An Iterative Approach

```{r echo = FALSE}
minutes_per_shallow_dive <- 30
minutes_per_medium_dive <- 120
minutes_per_deep_dive <- 4 * 60
```

I'll do each of these steps for each paper:

1. Read title and list of authors. Just to get a big-picture view of the publication areas.
1. Shallow dive. Read the abstract. Look at all figures / theorems. Try to identify the main result. Read intro/conclusion.
1. Medium dive. Skim the entire paper, skipping technical details. Make note of what I skipped that might be worth reading later.
1. Deep dive. Read end-to-end, including technical details except for proofs.
1. Deepest dive. Dig into proofs. Write some R code that captures some main point of the paper. See if I can reproduce in some simple version.


## Roadmap and Milestones


Here are the relevant dates:

* EC 2016 start date: `r ec_start_date`.
* Accepted papers announcement date: `r acceptance_date`. 
* Camera-ready due date: `r camera_ready_date`.
* Day I'll start reading: `r start_date`.
* I'll add in a `r days_buffer`-day buffer for delays or handling other urgent, unrelated things that might come up.
* Number of accepted papers: `r num_papers`.

In total, I'll have about **`r days_available` days** for reading/summarizing these papers. This means I'll have to average about **`r round(papers_per_day, 2)` papers per day** to get through them all.

Seeing the number, this actually seems pretty daunting, given I also have a full-time job. For each paper, I should make a quick list of what I want:

* What they did (something slightly more detailed than the abstract, but in my own words and in relation to other work I'm familiar with).
* The main contribution of this work.
* Any take-aways to investigate further, that might be applicable (e.g., proof techniques).
* Some questions for the authors. (Perhaps basic clarifying questions, if I'm unfamiliar with the area.)
* A list of papers to look at for background reading.


## Some TODOs

* Setup comments section so people can add their own insights / correct me where I'm wrong.
* Make sure I can write LaTeX in posts
* Make sure I can add images to posts
* Try a practice version with a few papers from EC 2015. (Both for figuring out how much time things take, as well as working out any kinks in the publishing process.)
* Figure out some ordering for reading papers that makes sense (by topic?)

